The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-10-09 JStatSoft_forestinventory_master-concordance.tex
update Andreas 09.10.2017(spelling errors)

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 107 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 115:%
1 97 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 213:%
123 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 223:%
1 71 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 295:%
134 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 307:%
1 110 1 1 4 1 1 1 2 1 0 2 1 3 0 1 2 2 1 1 3 14 0 1 2 16 1 1 5 7 0 1 2 4 1 1 2 24 0 1 2 6 1 1 2 4 0 1 2 4 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 126 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 7 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 823:%
147}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 824:%
1 101 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 162 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 10 0 1 2 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 6 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1251:%
149 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1263:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1328:%
162 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1338:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 18 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 21 1 1 3 5 0 1 2 28 1 1 3 5 0 1 2 40 1 1 3 5 0 1 2 25 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1624:%
173 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1634:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1865:%
184 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1874:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1879:%
194 11 1}

>>>>

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 107 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 115:%
1 97 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 213:%
123 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 218:%
1 69 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 288:%
129 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 293:%
1 104 1 1 4 1 1 1 2 1 0 2 1 3 0 1 2 2 1 1 3 14 0 1 2 16 1 1 5 7 0 1 2 4 1 1 2 24 0 1 2 6 1 1 2 4 0 1 2 4 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 126 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 7 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 803:%
135}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 804:%
1 92 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 150 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 10 0 1 2 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 6 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1210:%
137 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1215:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1280:%
143 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1285:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 12 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 13 1 1 3 5 0 1 2 28 1 1 3 5 0 1 2 40 1 1 3 5 0 1 2 25 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1557:%
149 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1562:%
1 11 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1784:%
155 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1789:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1794:%
161 11 1}

### 2017-10-09 JStatSoft_forestinventory_master.rnw
update Andreas 18.09.2017(2)
update Andreas 05.10.2017(2)
update Andreas 09.10.2017(spelling errors)

%% an abstract and keywords
\Abstract{
Forest inventories provide reliable and evidence-based information to assess the state and development of forests over time.  They typically consist of a random sample of plot locations in the forest that are assessed individually by hand. Due to the high costs of these terrestrial campaigns, remote sensing information available in high quantity and low costs (e.g. LiDAR, stereophotogrammetry, etc.) is frequently incorporated in the estimation process in order to reduce inventory costs or improve estimation precision. With respect to this objective, the application of \textit{multiphase} forest inventory methods (e.g. double- and triple-sampling regression estimators) has proved to be efficient. While these methods have been successfully applied in practice, the availability of open-source software has been rare if not non-existent. The \proglang{R} package \pkg{forestinventory} provides a comprehensive set of global and small area regression estimators for multiphase forest inventories under simple and cluster sampling. The implemented methods have been demonstrated in various scientific studies ranging from small to large scale forest inventories, and can be used for post-stratification, regression and regression within strata. This article summarizes the mathematical theory of this family of design-based estimators and demonstrates their application in \proglang{R}.}

@@

@@

% NOTES:
%
%
%
%

@@

% NOTES:
% - mention difference between finite and infinite population approach ?
%
%
%

@@

% \SweaveInput{rnw/Onephase_Estimators and their Application.Rnw}

@@

% NOTES:
%
%

@@

% NOTES:
%
%
%

@@

% -------------------------------------------------------------------------- %
\end{document}

>>>>

%% an abstract and keywords
\Abstract{
Forest inventories provide reliable evidence-based information to assess the state and development of forests over time.  They typically consist of a random sample of plot locations in the forest that are assessed individually by hand. Due to the high costs of these terrestrial campaigns, remote sensing information available in high quantity and low costs (e.g. LiDAR, stereophotogrammetry, etc.) is frequently incorporated in the estimation process in order to reduce inventory costs or improve estimation precision. With respect to this objective, the application of \textit{multi-phase} forest inventory methods (e.g. double- and triple-sampling regression estimators) has proved to be efficient. While these methods have been successfully applied in practice, the availability of open-source software has been rare if not non-existent. The \proglang{R} package \pkg{forestinventory} provides a comprehensive set of global and small area regression estimators for multiphase forest inventories under simple and cluster sampling. The implemented methods have been demonstrated in various scientific studies ranging from small to large scale forest inventories, and can be used for post-stratification, regression and regression within strata. This article summarizes the mathematical theory of this family of design-based estimators and demonstrates their application in \proglang{R}.}

@@

\setlength{\parindent}{1em} % Einzug bei neuen Absätzen

@@

@@

@@

@@

@@

@@

%------------------------------------------------------------------------------------------------%
\end{document}

### 2017-10-09 rnw/Analysis and Visualization.Rnw
update Andreas 09.10.2017(spelling errors)

% include:
% - estTable()-function demo
% - mphase.gain()-function demo
% - plot.esttable()-function demo
% - 3-4 pages max
% - pronounce that "it is crucial to quantify the potential benefit of the mphase procedures
%   compared to the onephase procedure --> allows to calculate the financial benefit --> rel.eff

@@

As mentioned in the introduction (section \ref{sec:intro}), the application of multi-phase estimation techniques in forest practice have two main \textbf{goals}:  
\begin{enumerate}
  \item \textit{\textbf{maintaining}} the one-phase estimation precision under reduced costs, i.e. reduced $s_2$ sample size
  \item \textit{\textbf{increasing}} the estimation precision at identical costs, i.e. without increasing the $s_2$ sample size
\end{enumerate}

>>>>

@@

As mentioned in the introduction (Section \ref{sec:intro}), the application of multi-phase estimation techniques in forest practice have two main \textbf{goals}:  
\begin{enumerate}
  \item \textit{\textbf{maintaining}} the one-phase estimation precision under reduced costs, i.e. reduced $s_2$ sample size
  \item \textit{\textbf{increasing}} the estimation precision at identical costs, i.e. without increasing the $s_2$ sample size
\end{enumerate}

### 2017-10-09 rnw/Introduction.Rnw
update Andreas 09.10.2017(spelling errors)

Terrestrial inventories have the benefit of being very flexible in the sense that they can be used to produce high quality estimates for a wide-variety of different forest attributes. However, they have the downside of being very expensive.  Improving the precision of the estimates by increasing the number of sample plots essentially means that travel costs will rise as trained inventorists are sent to more and more random plot locations. This is why the number of terrestrial samples is often limited. Although national inventories usually possess sufficient the terrestrial sample size to provide high estimation accuracies for larger areas, this is often not the case for smaller areas, such as forest management units.  As a result, there has been increasing need for alternative inventory methods that can maintain the same estimation precision at lower costs, or achieve higher estimation precision at identical costs \citep{vonluepke2013}. A method which has become particularly attractive is called \textit{multiphase sampling}. The core concept is to enlarge the sample size in order to gain higher estimation precision \textit{without} enlarging the terrestrial sample size. This is done by using predictions of the terrestrial target variable at additional sample locations where the terrestrial information has not been gathered. These predictions are produced by regression models that use explanatory variables derived from auxiliary data, commonly in the form of remote sensing data available in the inventory area in large sample or even wall-to-wall. Regression estimators using this concept can consider either \textit{one} additional sample of plot locations consisting of auxiliary information (two-phase or double-sampling) or \textit{two} additional samples available in different sample sizes (three-phase or triple-sampling) \citep{gregoire2007, saborowski2010, mandallaz2013a, mandallaz2013c, vonLüpke2012}. Their application to existing forest inventory systems have already showed their efficiency in terms of cost reduction and gain in estimation precision \citep{breidenbach2012, vonLuebke2014, mandallaz2013b, magnussen2014, massey2014a}.\par

>>>>

Terrestrial inventories have the benefit of being very flexible in the sense that they can be used to produce high quality estimates for a wide-variety of different forest attributes. However, they have the downside of being very expensive.  Improving the precision of the estimates by increasing the number of sample plots essentially means that travel costs will rise as trained inventorists are sent to more and more random plot locations. This is why the number of terrestrial samples is often limited. Although national inventories usually possess a sufficiently large terrestrial sample size to provide high estimation accuracies for larger areas, this is often not the case for smaller areas, such as forest management units.  As a result, there has been increasing need for alternative inventory methods that can maintain the same estimation precision at lower costs, or achieve higher estimation precision at identical costs \citep{vonluepke2013}. A method which has become particularly attractive is called \textit{multiphase sampling}. The core concept is to enlarge the sample size in order to gain higher estimation precision \textit{without} enlarging the terrestrial sample size. This is done by using predictions of the terrestrial target variable at additional sample locations where the terrestrial information has not been gathered. These predictions are produced by regression models that use explanatory variables derived from auxiliary data, commonly in the form of remote sensing data available in the inventory area in large sample or even wall-to-wall. Regression estimators using this concept can consider either \textit{one} additional sample of plot locations consisting of auxiliary information (two-phase or double-sampling) or \textit{two} additional samples available in different sample sizes (three-phase or triple-sampling) \citep{gregoire2007, saborowski2010, mandallaz2013a, mandallaz2013c, vonLüpke2012}. Their application to existing forest inventory systems have already showed their efficiency in terms of cost reduction and gain in estimation precision \citep{breidenbach2012, vonLuebke2014, mandallaz2013b, magnussen2014, massey2014a}.\par
